---
title: "Cycling Analytics"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: fill
    theme: 
      version: 4
      bootswatch: flatly
---

```{r setup, include=FALSE}
libs <- c("flexdashboard","tidyverse","plotly","leaflet","leaflet.extras","lubridate","mapdata")
purrr::walk(libs, ~library(.,character.only = T))

dashboard_stage <- function(stage_name, expr) {
  if (exists("run_dashboard_stage", mode = "function")) {
    run_dashboard_stage(stage_name, expr)
  } else {
    force(expr)
  }
}

con <- dashboard_stage("Connect database", {
  connect_db()
})

dashboard_stage("Load data", {
  activity_streams <- get_streams(con)

  activity_summary <- build_activity_summary(activity_streams)

  tbr_streams <- get_tbr_streams(con)

  tbr_activities <- tbr_streams |> 
    select(activity_id:moving_time_seconds) |> 
    distinct()

  ytd_stats <- build_ytd_stats(activity_streams)

  ytd_streams <- activity_streams |> filter(year(start_date_local) == year(Sys.Date()))

  position_extremities <- get_position_extremities(ytd_streams)

  best_power_efforts <- get_ytd_best_power_efforts(con)

  best_power_effort_streams <- get_best_effort_streams(con, best_power_efforts)
})
```

```{css, echo=FALSE}
#best-efforts .value-box {
  min-height: 92px;
}

#best-efforts .value-box .inner {
  padding: 10px 16px;
}

#best-efforts .value-box .value {
  margin-bottom: 2px;
}

#best-efforts .value-box .caption {
  margin-top: 0;
}

#best-efforts .value-box .icon {
  top: 8px;
  right: 14px;
  font-size: 56px;
}
```

Summary
===================================== 

Row
-----------------------------------------------------------------------

### `r str_glue('Last refresh: {format(Sys.time(), "%H:%M")}<br>','Next refresh: {format(get_next_dashboard_run(), "%H:%M")}'
)`

```{r}
valueBox(format(Sys.time(), "%d %b %y"), color = "#EDF0F1")
```

### `r str_glue('Miles this year<br>({get_ytd_values("distance_mi", ytd_stats)["pytd"]} pytd)')`

```{r}
get_ytd_valuebox("ytd_distance_mi", ytd_stats)
```

### `r str_glue('Projected miles this year<br>({get_ytd_values("ytd_predicted_distance_mi", ytd_stats)["pytd"]} pytd projected, {get_ytd_values("distance_mi", ytd_stats)["pyr"]} py total)')`

```{r}
get_ytd_valuebox("ytd_predicted_distance_mi", ytd_stats)
```

### `r str_glue('Tons this year<br>({get_ytd_values("tons", ytd_stats)["pytd"]} pytd, {get_ytd_values("tons", ytd_stats)["pyr"]} py total)')`

```{r}
get_ytd_valuebox("ytd_tons", ytd_stats)
```

### `r str_glue('Hours this year<br>({get_ytd_values("time_hr", ytd_stats)["pytd"]} pytd, {get_ytd_values("time_hr", ytd_stats)["pyr"]} py total)')`

```{r}
get_ytd_valuebox("ytd_time_hr", ytd_stats)
```

### `r str_glue('Longest ride this year (mi)<br>({get_ytd_values("longest_ride", ytd_stats)["pytd"]} pytd, {get_ytd_values("longest_ride", ytd_stats)["pyr"]} py max)')`

```{r}
get_ytd_valuebox("ytd_longest_ride", ytd_stats)
```

Row 
-----------------------------------------------------------------------

### `r str_glue("Miles, mi (vs {year(Sys.Date()) - 1})")`

```{r}
draw_ytd_curve("ytd_distance_mi", ytd_stats)
```

### `r str_glue("Elevation, m (vs {year(Sys.Date()) - 1})")`

```{r}
draw_ytd_curve("ytd_elevation_m", ytd_stats)
```

### `r str_glue("Tons (vs {year(Sys.Date()) - 1})")`

```{r}
draw_ytd_curve("ytd_tons", ytd_stats)
```

Row 
-----------------------------------------------------------------------

### Critical Power (vs all-time peaks)

```{r}
draw_critical_metric_curve("power", con)
```

Best Efforts
===================================== 

Row {data-height=95}
-----------------------------------------------------------------------

###

```{r}
get_best_effort_valuebox(best_power_efforts, 600)
```

###

```{r}
get_best_effort_valuebox(best_power_efforts, 1200)
```

###

```{r}
get_best_effort_valuebox(best_power_efforts, 1800)
```

###

```{r}
get_best_effort_valuebox(best_power_efforts, 3600)
```

Row {data-height=840}
-----------------------------------------------------------------------

###

```{r}
draw_best_effort_detail(best_power_effort_streams, best_power_efforts, 600)
```

###

```{r}
draw_best_effort_detail(best_power_effort_streams, best_power_efforts, 1200)
```

###

```{r}
draw_best_effort_detail(best_power_effort_streams, best_power_efforts, 1800)
```

###

```{r}
draw_best_effort_detail(best_power_effort_streams, best_power_efforts, 3600)
```

Trends
===================================== 

Row {data-height=150}
-----------------------------------------------------------------------

### Latest outdoor ride

```{r}
get_latest_ride_valuebox(activity_summary)
```

### `r str_glue("Goal progress ({get_annual_distance_goal_label(ytd_stats)})")`

```{r}
get_goal_progress_valuebox(ytd_stats)
```

### Goal pace

```{r}
get_goal_pace_valuebox(ytd_stats)
```

### Outdoor / indoor miles

```{r}
get_ride_mix_valuebox(activity_summary)
```

Row {data-height=850}
-----------------------------------------------------------------------

### Recent weekly training volume

```{r}
draw_weekly_training_volume(activity_summary)
```

Map
===================================== 

Row
-----------------------------------------------------------------------

### Most Northerly

```{r}
get_coord_valuebox("N", position_extremities)
```

### Most Southerly

```{r}
get_coord_valuebox("S", position_extremities)
```

### Most Easterly

```{r}
get_coord_valuebox("E", position_extremities)
```

### Most Westerly

```{r}
get_coord_valuebox("W", position_extremities)
```

Row
-----------------------------------------------------------------------

### `r str_glue("{year(Sys.Date())} tracks")`

```{r}
draw_map(ytd_streams)
```

tbr
===================================== 

Row
-----------------------------------------------------------------------

### tbr rides

```{r}
valueBox(nrow(tbr_activities), color = "#EDF0F1")
```

### Total tbr miles

```{r}

peaks_units |> filter(metric_name == "distance") |> mutate(value = sum(tbr_activities$distance_metres) * multiplier, value = str_glue("{round(value, digits = 1)} {units}")) |> pull(value) |> valueBox(color = "#EDF0F1")

```

### Longest tbr ride

```{r}
peaks_units |> filter(metric_name == "distance") |> mutate(value = max(tbr_activities$distance_metres) * multiplier, value = str_glue("{round(value, digits = 1)} {units}")) |> pull(value) |> valueBox(color = "#EDF0F1")
```

Row
-----------------------------------------------------------------------

### tbr tracks

```{r}
draw_map(tbr_streams)
```
