---
title: "Ride Summary"
subtitle: "Post-ride coaching report"
format:
  typst:
    papersize: a4
    fig-format: png
    margin:
      x: 15mm
      y: 14mm
    fontsize: 9pt
execute:
  echo: false
  warning: false
  message: false
params:
  activity_id: null
  project_root: "."
  ftp_watts: null
  session_objective: null
  rider_notes: null
  coach_observations: null
---

```{r}
#| label: setup
#| include: false
suppressPackageStartupMessages({
  library(tidyverse)
  library(lubridate)
  library(DBI)
  library(RMariaDB)
})

if (is.null(params$activity_id) || !nzchar(as.character(params$activity_id))) {
  stop("The ride summary requires an activity_id parameter.", call. = FALSE)
}
project_root <- normalizePath(params$project_root, mustWork = TRUE)
source(file.path(project_root, "db", "db.R"))
source(file.path(project_root, "reports", "ride-summary", "R", "ride_report_data.R"))
source(file.path(project_root, "reports", "ride-summary", "R", "ride_report_model.R"))
source(file.path(project_root, "reports", "ride-summary", "R", "ride_report_components.R"))

con <- connect_db()
ride_data <- load_ride_report_data(con, params$activity_id)
DBI::dbDisconnect(con)
activity <- ride_data$activity
streams <- ride_data$streams
best_efforts <- ride_data$best_efforts
laps <- ride_data$laps
continuous_best_efforts <- filter_continuous_efforts(best_efforts)
ftp_watts <- as.numeric(params$ftp_watts %||% NA_real_)
session_objective <- params$session_objective %||%
  Sys.getenv("RIDE_REPORT_SESSION_OBJECTIVE", unset = "")
rider_notes <- params$rider_notes %||%
  Sys.getenv("RIDE_REPORT_RIDER_NOTES", unset = "")
coach_observations <- params$coach_observations %||%
  Sys.getenv("RIDE_REPORT_COACH_OBSERVATIONS", unset = "")
lap_model <- prepare_lap_presentation_model(laps, streams, activity)
selected_efforts <- select_coaching_efforts(lap_model) |>
  prepare_coaching_effort_presentation()
recovery_intervals <- summarise_recovery_intervals(
  lap_model,
  selected_efforts
)
zone_data <- build_power_zones(streams, ftp_watts)
```

**Session objective:** `r ifelse(nzchar(session_objective), session_objective, "Not documented")`

```{r}
#| results: asis
rider_note_lines <- split_report_notes(rider_notes)
if (length(rider_note_lines) > 0L) {
  cat("\n**Rider notes:**\n\n")
  cat(paste0("- ", rider_note_lines, collapse = "\n"), "\n")
}
```

# Ride overview

```{r}
#| results: asis
summary_cards(list(
  Date = format(as.Date(activity$start_date_local[[1]]), "%d %B %Y"),
  `Start time` = format(
    as.POSIXct(activity$start_datetime_local[[1]]),
    "%H:%M"
  ),
  Activity = activity$activity_name[[1]] %||% "Unnamed ride",
  Bike = "Not available",
  Distance = format_metric(
    activity$distance_metres[[1]] * 0.000621371,
    " mi",
    1
  ),
  `Moving time` = format_duration(activity$moving_time_seconds[[1]]),
  `Elapsed time` = format_duration(activity$elapsed_time_seconds[[1]]),
  `Elevation gain` = format_metric(activity$elevation_gain_metres[[1]], " m"),
  `Average speed` = format_metric(
    activity$average_speed_miles_per_hour[[1]], " mph", 1
  )
))
```

# Power and cardiovascular summary

```{r}
#| results: asis
summary_cards(list(
  `Average power` = format_metric(
    activity$average_power_watts[[1]],
    " W"
  ),
  `Maximum power` = format_metric(safe_max(streams$watts), " W"),
  Work = format_metric(activity$energy_kilojoules[[1]], " kJ"),
  `Average HR` = format_metric(activity$average_heartrate_bpm[[1]], " bpm"),
  `Maximum HR` = format_metric(safe_max(streams$heartrate_bpm), " bpm"),
  `Average cadence` = format_metric(
    activity$average_cadence_rpm[[1]], " rpm"
  ),
  `Maximum cadence` = format_metric(safe_max(streams$cadence_rpm), " rpm")
))
```

# Conditions

```{r}
#| results: asis
summary_cards(list(
  `Average temperature` = format_metric(
    safe_mean(streams$temperature_celsius), " C", 1
  ),
  `Maximum temperature` = format_metric(
    safe_max(streams$temperature_celsius), " C", 1
  ),
  `Wind speed` = "Not available",
  `Wind direction` = "Not available"
))
```

# Laps

```{r}
#| results: asis
lap_table <- format_lap_summary_table(lap_model)
if (nrow(lap_table) == 0L) {
  cat("No canonical laps are available for this activity.")
} else {
  print(compact_table(lap_table))
}
```

```{r}
#| results: asis
if (nrow(selected_efforts) > 0L) {
  cat("```{=typst}\n#pagebreak()\n```\n\n")
}
```

# Selected Coaching Efforts

```{r}
#| results: asis
if (nrow(selected_efforts) == 0L) {
  boundaries_available <- nrow(lap_model) > 0L && any(
    !is.na(lap_model$start_time_seconds) &
      !is.na(lap_model$end_time_seconds)
  )
  if (!boundaries_available && nrow(lap_model) > 0L) {
    cat(
      "Canonical lap time boundaries are unavailable for this ride.\n\n",
      "Individual coaching efforts could not be evaluated. The complete ",
      "canonical lap summary remains available above."
    )
  } else {
    cat(
      "No individual coaching efforts were selected for detailed review.\n\n",
      "This ride consisted primarily of steady pacing or did not contain ",
      "laps meeting the current selection criteria."
    )
  }
}
```

```{r}
#| results: asis
if (nrow(selected_efforts) > 0L) {
  cat("## Interval summary\n\n")
  print(compact_table(format_coaching_effort_summary_table(selected_efforts)))

  recovery_table <- format_recovery_summary_table(recovery_intervals)
  if (nrow(recovery_table) > 0L) {
    cat("\n\n## Recovery summary\n\n")
    print(compact_table(recovery_table))
  }
  cat("```{=typst}\n#pagebreak()\n```\n\n")
}
```

```{r}
#| label: effort-page-1
#| results: asis
#| fig-width: 6.8
#| fig-height: 4.8
if (nrow(selected_efforts) >= 1L) {
  render_coaching_effort_page(selected_efforts[1, ], streams)
}
```

```{r}
#| results: asis
if (nrow(selected_efforts) >= 2L) {
  cat("```{=typst}\n#pagebreak()\n```\n\n")
}
```

```{r}
#| label: effort-page-2
#| results: asis
#| fig-width: 6.8
#| fig-height: 4.8
if (nrow(selected_efforts) >= 2L) {
  render_coaching_effort_page(selected_efforts[2, ], streams)
}
```

```{r}
#| results: asis
if (nrow(selected_efforts) >= 3L) {
  cat("```{=typst}\n#pagebreak()\n```\n\n")
}
```

```{r}
#| label: effort-page-3
#| results: asis
#| fig-width: 6.8
#| fig-height: 4.8
if (nrow(selected_efforts) >= 3L) {
  render_coaching_effort_page(selected_efforts[3, ], streams)
}
```

```{r}
#| results: asis
if (nrow(selected_efforts) >= 4L) {
  cat("```{=typst}\n#pagebreak()\n```\n\n")
}
```

```{r}
#| label: effort-page-4
#| results: asis
#| fig-width: 6.8
#| fig-height: 4.8
if (nrow(selected_efforts) >= 4L) {
  render_coaching_effort_page(selected_efforts[4, ], streams)
}
```

```{r}
#| results: asis
if (nrow(selected_efforts) >= 5L) {
  cat("```{=typst}\n#pagebreak()\n```\n\n")
}
```

```{r}
#| label: effort-page-5
#| results: asis
#| fig-width: 6.8
#| fig-height: 4.8
if (nrow(selected_efforts) >= 5L) {
  render_coaching_effort_page(selected_efforts[5, ], streams)
}
```

```{r}
#| results: asis
if (nrow(selected_efforts) >= 6L) {
  cat("```{=typst}\n#pagebreak()\n```\n\n")
}
```

```{r}
#| label: effort-page-6
#| results: asis
#| fig-width: 6.8
#| fig-height: 4.8
if (nrow(selected_efforts) >= 6L) {
  render_coaching_effort_page(selected_efforts[6, ], streams)
}
```

```{r}
#| results: asis
if (nrow(selected_efforts) >= 7L) {
  cat("```{=typst}\n#pagebreak()\n```\n\n")
}
```

```{r}
#| label: effort-page-7
#| results: asis
#| fig-width: 6.8
#| fig-height: 4.8
if (nrow(selected_efforts) >= 7L) {
  render_coaching_effort_page(selected_efforts[7, ], streams)
}
```

```{r}
#| results: asis
if (nrow(selected_efforts) >= 8L) {
  cat("```{=typst}\n#pagebreak()\n```\n\n")
}
```

```{r}
#| label: effort-page-8
#| results: asis
#| fig-width: 6.8
#| fig-height: 4.8
if (nrow(selected_efforts) >= 8L) {
  render_coaching_effort_page(selected_efforts[8, ], streams)
}
```

```{r}
#| results: asis
if (nrow(selected_efforts) >= 9L) {
  cat("```{=typst}\n#pagebreak()\n```\n\n")
}
```

```{r}
#| label: effort-page-9
#| results: asis
#| fig-width: 6.8
#| fig-height: 4.8
if (nrow(selected_efforts) >= 9L) {
  render_coaching_effort_page(selected_efforts[9, ], streams)
}
```

```{r}
#| results: asis
if (nrow(selected_efforts) >= 10L) {
  cat("```{=typst}\n#pagebreak()\n```\n\n")
}
```

```{r}
#| label: effort-page-10
#| results: asis
#| fig-width: 6.8
#| fig-height: 4.8
if (nrow(selected_efforts) >= 10L) {
  render_coaching_effort_page(selected_efforts[10, ], streams)
}
```

```{r}
#| results: asis
if (nrow(selected_efforts) > 0L) {
  cat("```{=typst}\n#pagebreak()\n```\n\n")
}
```

# Ride plots

```{r}
#| fig-width: 7.2
#| fig-height: 2.1
ride_plots <- list(
  plot_ride_metric(
    streams, "altitude_metres", "Elevation profile", "Elevation (m)",
    report_colours$elevation, "#D7E3D2"
  ),
  plot_ride_metric(
    streams,
    "watts",
    "Power trace",
    "Power (W)",
    report_colours$ink,
    highlighted_efforts = selected_efforts
  ),
  plot_ride_metric(
    streams, "heartrate_bpm", "Heart-rate trace", "Heart rate (bpm)",
    report_colours$heart
  )
)
for (plot in ride_plots) if (!is.null(plot)) print(plot)
```

# Power distribution

```{r}
#| fig-width: 7.2
#| fig-height: 2.8
zone_plot <- plot_power_zones(zone_data)
if (is.null(zone_plot)) {
  cat("Power-zone time unavailable: supply a current FTP to enable it.")
} else print(zone_plot)

curve_plot <- plot_ride_power_curve(continuous_best_efforts)
if (is.null(curve_plot)) {
  cat("Ride-only power-duration data unavailable.")
} else print(curve_plot)
```

# Best powers

```{r}
#| results: asis
best_power_table <- tibble(
  duration_seconds = c(5, 60, 300, 1200, 3600),
  Duration = c("5 s", "1 min", "5 min", "20 min", "60 min")
) |>
  left_join(
    continuous_best_efforts |> select(duration_seconds, peak_value),
    by = "duration_seconds"
  ) |>
  transmute(
    Duration,
    `Best power` = map_chr(peak_value, format_metric, suffix = " W")
  )
print(compact_table(best_power_table))
```

```{=typst}
#pagebreak()
```

# Coaching prompts

- Which selected effort best reflects the purpose of the ride?
- Was power delivery appropriately steady for the terrain and session goal?
- How did heart rate respond during the longer effort windows?
- Did cadence remain effective as fatigue accumulated?
- Were fuelling and hydration appropriate for the ride duration and intensity?
- Which missing context - perceived exertion, weather, route or session intent -
  would most change the interpretation?

# Coach observations

```{r}
#| results: asis
observation_lines <- split_report_notes(coach_observations)
if (length(observation_lines) == 0L) {
  cat("No coach observations documented.")
} else {
  cat(paste0("- ", observation_lines, collapse = "\n"))
}
```

# Session diagnostics

- **Pacing:** Coach/rider assessment required
- **Fuelling:** Coach/rider assessment required

These are discussion checks, not calculated judgements. Trusted diagnostic and
fuelling products do not yet exist.

# Data provenance and limitations

- Activity summaries and streams: `cycling_platform_silver`.
- Lap summaries and effort boundaries: `cycling_platform_silver.activity_laps`.
- Best-power windows: `cycling_platform_gold.activity_best_efforts`.
- Gold effort windows whose elapsed span exceeds their requested duration are
  excluded. The platform must provide the next valid continuous window before
  that duration can appear in this report.
- Estimated NP, VI, IF and TSS are deliberately omitted pending canonical
  platform products.
- Lap VAM, effort selection and zones are isolated report-only presentation
  calculations, not canonical platform facts.
- Bike name requires an agreed bike-library interface.
- Wind, detected climbs/intervals, FTP history,
  training-load metrics and HR-power decoupling are not currently available as
  trusted platform products.
