---
title: "Ride Summary"
subtitle: "Post-ride coaching report"
format:
  typst:
    papersize: a4
    fig-format: png
    margin:
      x: 15mm
      y: 14mm
    fontsize: 9pt
execute:
  echo: false
  warning: false
  message: false
params:
  activity_id: null
  project_root: "."
  ftp_watts: null
  session_objective: null
---

```{r}
#| label: setup
#| include: false
suppressPackageStartupMessages({
  library(tidyverse)
  library(lubridate)
  library(DBI)
  library(RMariaDB)
})

if (is.null(params$activity_id) || !nzchar(as.character(params$activity_id))) {
  stop("The ride summary requires an activity_id parameter.", call. = FALSE)
}
project_root <- normalizePath(params$project_root, mustWork = TRUE)
source(file.path(project_root, "db", "db.R"))
source(file.path(project_root, "reports", "ride-summary", "R", "ride_report_data.R"))
source(file.path(project_root, "reports", "ride-summary", "R", "ride_report_model.R"))
source(file.path(project_root, "reports", "ride-summary", "R", "ride_report_components.R"))

con <- connect_db()
ride_data <- load_ride_report_data(con, params$activity_id)
DBI::dbDisconnect(con)
activity <- ride_data$activity
streams <- ride_data$streams
best_efforts <- ride_data$best_efforts
continuous_best_efforts <- filter_continuous_efforts(best_efforts)
ftp_watts <- as.numeric(params$ftp_watts %||% NA_real_)
session_objective <- params$session_objective %||%
  Sys.getenv("RIDE_REPORT_SESSION_OBJECTIVE", unset = "")
selected_efforts <- select_coaching_efforts(continuous_best_efforts)
zone_data <- build_power_zones(streams, ftp_watts)
```

**Session objective:** `r ifelse(nzchar(session_objective), session_objective, "Not supplied")`

# Ride overview

```{r}
#| results: asis
summary_cards(list(
  Date = format(as.Date(activity$start_date_local[[1]]), "%d %B %Y"),
  `Start time` = format(
    as.POSIXct(activity$start_datetime_local[[1]]),
    "%H:%M"
  ),
  Activity = activity$activity_name[[1]] %||% "Unnamed ride",
  Bike = "Not available",
  Distance = format_metric(
    activity$distance_metres[[1]] * 0.000621371,
    " mi",
    1
  ),
  `Moving time` = format_duration(activity$moving_time_seconds[[1]]),
  `Elapsed time` = format_duration(activity$elapsed_time_seconds[[1]]),
  `Elevation gain` = format_metric(activity$elevation_gain_metres[[1]], " m"),
  `Average speed` = format_metric(
    activity$average_speed_miles_per_hour[[1]], " mph", 1
  )
))
```

# Power and cardiovascular summary

```{r}
#| results: asis
summary_cards(list(
  `Average power` = format_metric(
    activity$average_power_watts[[1]],
    " W"
  ),
  `Maximum power` = format_metric(safe_max(streams$watts), " W"),
  Work = format_metric(activity$energy_kilojoules[[1]], " kJ"),
  `Average HR` = format_metric(activity$average_heartrate_bpm[[1]], " bpm"),
  `Maximum HR` = format_metric(safe_max(streams$heartrate_bpm), " bpm"),
  `Average cadence` = format_metric(
    activity$average_cadence_rpm[[1]], " rpm"
  ),
  `Maximum cadence` = format_metric(safe_max(streams$cadence_rpm), " rpm")
))
```

# Conditions

```{r}
#| results: asis
summary_cards(list(
  `Average temperature` = format_metric(
    safe_mean(streams$temperature_celsius), " C", 1
  ),
  `Maximum temperature` = format_metric(
    safe_max(streams$temperature_celsius), " C", 1
  ),
  `Wind speed` = "Not available",
  `Wind direction` = "Not available"
))
```

# Laps

Lap analysis is intentionally unavailable until cycling-platform publishes a
curated lap product with distance, time, power, NP, heart rate, cadence, speed
and elevation gain.

```{r}
#| results: asis
if (nrow(selected_efforts) > 0L) {
  cat("```{=typst}\n#pagebreak()\n```\n\n")
}
```

# Key efforts

```{r}
#| results: asis
if (nrow(selected_efforts) == 0L) {
  cat(
    "No eligible Best 20 min effort is available for this ride. ",
    "Longest/highest-NP/fastest climb selection requires a trusted climb product."
  )
}
```

```{r}
#| label: effort-pages
#| results: asis
#| fig-width: 7.2
#| fig-height: 2.25
if (nrow(selected_efforts) > 0L) {
  for (effort_index in seq_len(nrow(selected_efforts))) {
    effort_model <- build_effort_summary(selected_efforts[effort_index, ], streams)
    effort_summary <- effort_model$summary
    effort_plots <- plot_effort_traces(
      effort_model$context_streams, effort_summary$name[[1]]
    )
    cat("## ", effort_summary$name[[1]], "\n\n", sep = "")
    summary_cards(list(
      Distance = format_metric(effort_summary$distance_miles, " mi", 1),
      Duration = format_duration(effort_summary$duration_seconds),
      `Average power` = format_metric(effort_summary$average_power_watts, " W"),
      `Average HR` = format_metric(
        effort_summary$average_heartrate_bpm, " bpm"
      ),
      `Average cadence` = format_metric(
        effort_summary$average_cadence_rpm, " rpm"
      ),
      `Estimated elevation gain*` = format_metric(
        effort_summary$elevation_gain_metres, " m"
      ),
      `Estimated VAM*` = format_metric(
        effort_summary$vam_metres_per_hour, " m/h"
      )
    ))
    cat("\n\n")
    if (!is.null(effort_plots)) {
      print(effort_plots$power)
      print(effort_plots$elevation)
    }
    cat(
      "\n\n*Elevation gain and VAM are report estimates. ",
      "The effort window and average power come from Gold best efforts.*\n\n"
    )
    cat("The shaded region is the effort; the trace includes 30 s context.\n\n")
    if (effort_index < nrow(selected_efforts)) {
      cat("```{=typst}\n#pagebreak()\n```\n\n")
    }
  }
  cat("```{=typst}\n#pagebreak()\n```\n\n")
}
```

# Ride plots

```{r}
#| fig-width: 7.2
#| fig-height: 2.1
ride_plots <- list(
  plot_ride_metric(
    streams, "altitude_metres", "Elevation profile", "Elevation (m)",
    report_colours$elevation, "#D7E3D2"
  ),
  plot_ride_metric(
    streams,
    "watts",
    "Power trace",
    "Power (W)",
    report_colours$ink,
    highlighted_efforts = selected_efforts
  ),
  plot_ride_metric(
    streams, "heartrate_bpm", "Heart-rate trace", "Heart rate (bpm)",
    report_colours$heart
  )
)
for (plot in ride_plots) if (!is.null(plot)) print(plot)
```

# Power distribution

```{r}
#| fig-width: 7.2
#| fig-height: 2.8
zone_plot <- plot_power_zones(zone_data)
if (is.null(zone_plot)) {
  cat("Power-zone time unavailable: supply a current FTP to enable it.")
} else print(zone_plot)

curve_plot <- plot_ride_power_curve(continuous_best_efforts)
if (is.null(curve_plot)) {
  cat("Ride-only power-duration data unavailable.")
} else print(curve_plot)
```

# Best powers

```{r}
#| results: asis
best_power_table <- tibble(
  duration_seconds = c(5, 60, 300, 1200, 3600),
  Duration = c("5 s", "1 min", "5 min", "20 min", "60 min")
) |>
  left_join(
    continuous_best_efforts |> select(duration_seconds, peak_value),
    by = "duration_seconds"
  ) |>
  transmute(
    Duration,
    `Best power` = map_chr(peak_value, format_metric, suffix = " W")
  )
print(compact_table(best_power_table))
```

```{=typst}
#pagebreak()
```

# Coaching prompts

- Which selected effort best reflects the purpose of the ride?
- Was power delivery appropriately steady for the terrain and session goal?
- How did heart rate respond during the longer effort windows?
- Did cadence remain effective as fatigue accumulated?
- Were fuelling and hydration appropriate for the ride duration and intensity?
- Which missing context - perceived exertion, weather, route or session intent -
  would most change the interpretation?

# Session diagnostics

- **Pacing:** Coach/rider assessment required
- **Fuelling:** Coach/rider assessment required

These are discussion checks, not calculated judgements. Trusted diagnostic and
fuelling products do not yet exist.

# Data provenance and limitations

- Activity summaries and streams: `cycling_platform_silver`.
- Best-power windows: `cycling_platform_gold.activity_best_efforts`.
- Gold effort windows whose elapsed span exceeds their requested duration are
  excluded. The platform must provide the next valid continuous window before
  that duration can appear in this report.
- Laps are omitted pending a curated platform product.
- Estimated NP, VI, IF and TSS are deliberately omitted pending canonical
  platform products.
- Effort elevation gain, VAM and zones are isolated report-only calculations,
  not canonical platform facts.
- Bike name requires an agreed bike-library interface.
- Wind, detected climbs/intervals, FTP history,
  training-load metrics and HR-power decoupling are not currently available as
  trusted platform products.
